Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-03 submission.tex
Added preliminary intro

\section{Introduction}
\label{sec:intro}

>>>>

\section{Introduction}
\label{sec:intro}
PoS tagging is an important preprocessing step for many NLP
tasks, such as parsing, named entity recognition and sentiment
analysis. Whereas much effort has gone into the development of
PoS-taggers, to the effect that this task is often considered
more or less a solved task, considerably less effort has been
devoted to the empirical evaluation of the PoS tag sets
themselves. 
PoS tag sets are usually employed in a "one size fits
all" fashion, regardless of the requirements posed by the
downstream NLP tasks for which PoS-tagging is performed.

It is well known that syntactic parsing often benefits from quite
fine-grained morphological distinctions. However, in a realistic
setting where the aim is to parse raw text, this will often
require a separate step of morphological analysis in addition to
PoS-tagging that can be quite expensive.

In this paper, we optimize a Norwegian PoS tag set for the task of
data-driven dependency parsing.  We show that the introduction of
morphological distinctions not present in the original tag set, whilst
compromising tagger accuracy, actually leads to significantly improved
parsing accuracy.

The article is structured as follows. We start out by reviewing
previous work on tag set evaluation in Section \ref{sec:prev} and
